Genetic Algorithm Based Formula Generation for Curve Fitting in Time Series Forecasting Implemented as Mobile Distributed Computing

### 2019-05-01 Genetic-Algorithm-Based-Formula-Generation-for-Curve-Fitting-in-Time-Series-Forecasting-Implemented-as-Mobile-Distributed-Computing/paper.tex
General part of the introduction was written.

@@

>>>>

Distributed computing is a computational organization in a system where components are located on different networked computers \cite{balabanov01}. These computers communicates and coordinates their activities by passing messages between each other. Distributed computing is remarkable with: concurrency of components, lack of a global clock, and independent failure of components. In distributed computing, a problem is divided into many tasks, each of which is solved by one or more computers \cite{godfrey01}, which communicate with each other via message passing \cite{andrews01}. Distributed computing is generally used for solving a large computational problems.

In this study for distributed computing will be accepted the definition which states that each processor has its own memory and it is embedded in separate device. Under this conditions calculating instructions run in parallel, which is the only relation with the parallel computing. The system is tolerant to a single component failure. The exact structure of the system is not know in advance and it changes with the time passing, because some nodes get in when some nodes get out \cite{balabanov02}. The whole system consists of heterogeneous hardware and variety types of network connectivity.

When end users donate their computational resources it is called donated distributed computing and in most cases computations are organized as screensaver applications or low consumption demon processes. Many devices around the world have periods of idle usage. In such cases their owners are capable to donate this calculating power. Donated calculating power is mainly used for low budget projects usually in society help. Many scientific projects are organized around donated distributed computing and the most popular of them is SETI@home, which analyzes radio signals from the deep space.

Last decade was marked with huge progress of mobile devices and communications, which gave to the scientist new capabilities for implementation of distributed computing software implementation. For example modern mobile devices are capable to provide active wallpapers instead of screensavers. Another option are the widgets supported in the modern mobile operating systems. But the best advantage of the mobile distributed computing is that most of the devices are operating 24/7, which is not the case with the desktop computers and working stations.

@@

\bibitem{balabanov01} Balabanov, T., Genova, K., \textbf{\textit{Distributed System for Artificial Neural Networks Training Based on Mobile Devices}}, Proceedings of International Conference AUTOMATICS AND INFORMATICS, Federation of the Scientific Engineering Unions John Atanasoff Society of Automatics and Informatics, p. 49--52, 2016.

\bibitem{godfrey01} Godfrey, B., \textbf{\textit{A primer on distributed computing}}, http://billpg.com/bacchae-co-uk/docs/dist.html Last visited: 01-May-2019 16:07:00 EET, 2006.

\bibitem{andrews01} Andrews, G., \textbf{\textit{Foundations of Multithreaded, Parallel, and Distributed Programming}}, Addison–Wesley, p. 291--292, 2000.

\bibitem{balabanov02} Balabanov, T., Zankinski, I., Barova, M., \textbf{\textit{Strategy for Individuals Distribution by Incident Nodes Participation in Star Topology of Distributed Evolutionary Algorithms}}, Cybernetics and Information Technologies, \textbf{16}(1), p. 80--88, 2016.
